---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rdviewer

<!-- badges: start -->
<!-- badges: end -->

rdviewer provides a user-friendly print method for parsed Rd files that helps visualising their structure

## Installation

You can install the development version of rdviewer from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("eliocamp/rdviewer")
```

## Example

We can get the parsed documentation by calling `utils:::.getHelpFile` on the results of `help`. 
The result is a deeply nested list with text and tags as attributes 

```{r}
help <- help("mean", package = "base")
rd <- utils:::.getHelpFile(help[1])
str(rd[[7]])  # Just one element
```

The default print method hides all that and prints a approximate representation of the original .Rd file

```{r}
rd
```
rdviewer replaces that with a tree that more closely matches the actual representation of the object

```{r}
library(rdviewer)  # Just load with library
```

And then print 

```{r}
rd
```

